\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\date{August, 2014}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                         Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\LARGE \textbf{Tony Enrique Lattke Urbaneja}}

Buntentorsteinweg 305  \ \ \textbullet
\ \  28201 Bremen - Germany
\\
+49 174 941 63 40 \ \ \textbullet \ \  \href{http://tony.lattke.org}{tony.lattke.org} \ \ \textbullet \ \ \href{mailto:tonylattke@gmail.com}{\nolinkurl{<tonylattke@gmail.com>}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                       Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em


\item
  \headerrow
  {\textbf{Lo mas Trendy}}
  {\textbf{Miranda, Ve}}
  \\

  \headerrow
  {\emph{Web developer}}
  {\emph{08/2013 -- 11/2013}}
  \begin{itemize*}
  \item Develop a web application using python Django, CSS, HTML5 and Javascript.
  \item Using Twython a tool of Twitter.
  \end{itemize*}

\item
  \headerrow
  {\textbf{Universidad Simón Bolívar}}
  {\textbf{Miranda, Ve}}
  \\
  
  \headerrow
  {\emph{\href{http://clei2013.org.ve/en}{CLEI 2013} (Computer Congress) - Collaborator}}
  {\emph{10/2013 -- 10/2013}}
  \begin{itemize*}
  \item Support in Committee logistic.
  \end{itemize*}

  \headerrow
  {\emph{\href{http://joincic.com.ve}{Joincic} (Computer Congress) - Head Cordinator}}
  {\emph{09/2011 -- 09/2013}}
  \begin{itemize*}
  \item Team organization and sponsor companies contact.
  \end{itemize*}
  
  \headerrow
  {\emph{\href{http://usbceic.ldc.usb.ve}{Computing Engineer Student Center} - Collaborator}}
  {\emph{09/2012 -- 09/2013}}
  \begin{itemize*}
  \item Support for the new president. 
  \item Event planning computer career.
  \item Sales service intended for the collection 
	of resources for students of computer center.
  \end{itemize*}
  
  \headerrow
  {\emph{\href{http://usbceic.ldc.usb.ve}{Computing Engineer Student Center} - President}}
  {\emph{07/2011 -- 07/2012}}
  \begin{itemize*}
  \item Event planning computer career.
  \item Sales service intended for the collection 
	of resources for students of computer center.
  \item Implementation of system to improve revenue management.
  \end{itemize*}

  \headerrow
  {\emph{\href{http://joincic.com.ve}{Joincic} (Computer Congress) - Collaborator}}
  {\emph{09/2010 -- 09/2011}}
  \begin{itemize*}
  \item Managing and maintaining event website.
  \end{itemize*}
  
  \headerrow
  {\emph{\href{http://usbceic.ldc.usb.ve}{Computing Engineer Student Center} - Collaborator}}
  {\emph{09/2010 -- 07/2011}}
  \begin{itemize*}
  \item Event planning computer career.
  \item Sales service intended for the collection 
	of resources for students of computer center.
  \end{itemize*}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Formal education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hrule
\vspace{-0.4em}
\subsection*{Formal education}

\begin{itemize}
	\parskip=0.1em

\item 
   \headerrow
   {\textbf{Universidad Simón Bolívar}}
   {\textbf{Miranda, Ve}}
	\\
	\headerrow
   {\emph{Computing Engineer}}
   {\emph{09/2007 -- 09/2013}}
   
   
   {\emph{- Specialization:}}
   \\
   {\emph{     Computer graphics}}
   \\
   {\emph{     Artificial intelligence}}
   \\
   {\emph{     Design and implementation of programming languages}}
   \\
   \\
   {\emph{- Electives:}}
   \\
   {\emph{     Artificial intelligence for Video games}}
   \\
   {\emph{     Introduction to Robotics}}
   \\
   {\emph{     Topics in Computer graphics in Video games}}
   \\
   \\
   {\emph{- Thesis Research Topic. The project obtained an “Exceptionally good” mention:}}
   \\
   {\emph{     Random content generation based on constraints}}

 \item 
   \headerrow
   {\textbf{U.E. Instituto Humanitas}}
   {\textbf{Dtto. Capital, Ve}}
	\\
	\headerrow
   {\emph{Bachelor of Science}}
   {\emph{09/2002 -- 09/2007}}
	\\
	\headerrow
   {\emph{Recognition of outstanding student}}
   {\emph{2007}}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Conferences
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Conferences}

\begin{itemize}
  \parskip=0.1em
\item 
   \headerrow
   {\textbf{Random content generation based on constraints, \emph{\href{http://www.concisa.net.ve/2014/}{CoNCISa 2014 (Computer Congress)}}}}
   {\textbf{Caracas, Ve}}
  \\
  \headerrow
   {Authors: Isaac López, Tony Lattke \& Carlos Pérez (Tutor)}{}
\end{itemize}

%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Awards}

\begin{itemize}
  \parskip=0.1em
\item 
   \headerrow
   {\textbf{First place of Thesis Research Topic in \emph{\href{http://www.concisa.net.ve/2014/}{CoNCISa 2014 (Computer Congress)}}}}
   {\textbf{Caracas, Ve}}
  \\
  \headerrow
   {Authors: Isaac López, Tony Lattke \& Carlos Pérez (Tutor)}{}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\vspace{-0.4em}
\subsection*{Certifications}

\begin{itemize}
	\parskip=0.1em
\item 
   \headerrow
   {\textbf{Miriadax}}
   {\textbf{Online Course}}
  \\
  \headerrow
   {\emph{Introduction to Business Intelligence}}
   {\emph{01/2015 -- 02/2015}}
  \\
  \headerrow
   {\emph{Marketing Strategies Online. Community Manager}}
   {\emph{01/2015 -- 02/2015}}
  \\
  \headerrow
   {\emph{Introduction to film language}}
   {\emph{12/2014}}
\item 
   \headerrow
   {\textbf{VFX Latino América}}
   {\textbf{Miranda, Ve}}
  \\
  \headerrow
   {\emph{Visual Effects and 3D Animation workshop}}
   {\emph{11/2013 -- 02/2014}}

\item 
   \headerrow
   {\textbf{Instituto Arts}}
   {\textbf{Miranda, Ve}}
	\\
	\headerrow
   {\emph{After Effects CS5.5}}
   {\emph{09/2011}}
	\\
	\headerrow
   {\emph{3D Studio Max 2009 - Animation and Design of characters}}
   {\emph{03/2010}}
	\\
	\headerrow
   {\emph{3D Studio Max 2009}}
   {\emph{12/2009}}
	\\
	\headerrow
   {\emph{Autocad 3D 2006 }}
   {\emph{08/2006}}
	\\
	\headerrow
   {\emph{Autocad 2D 2006}}
   {\emph{07/2005}}

\item 
   \headerrow
   {\textbf{Uneweb}}
   {\textbf{Miranda, Ve}}
	\\
	\headerrow
   {\emph{Blender}}
   {\emph{2010}}
\end{itemize}

%\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                       Contests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hrule
\vspace{-0.4em}
\subsection*{Contests}

\begin{itemize}
	\parskip=0.1em
\item 
   \headerrow
   {\textbf{Global Gamejam 2015}}
   {\textbf{Bremen, De}}
  \\
  \headerrow
   {\emph{\href{http://globalgamejam.org/2015/games/path-blank}{Path in blank}}}{}
\item 
   \headerrow
   {\textbf{Caracas Gamejam 2013}}
   {\textbf{Miranda, Ve}}
	\\
	\headerrow
   {\emph{\href{http://globalgamejam.org/2013/enter-panic-heart-attack}{Enter The Panic: Heart Attack}}}{}
\item 
   \headerrow
   {\textbf{Caracas Gamejam 2011}}
   {\textbf{Miranda, Ve}}
	\\
	\headerrow
   {\emph{\href{http://archive.globalgamejam.org/2011/enter-panic-attack-matus}{Enter The Panic: The Attack of Matus}}}{}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Knowledges
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hrule
\vspace{-0.4em}
\subsection*{Knowledges}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	
\item[Languages:]
  Spanish (Native language), English (B2), German (A2)
\item[Programming Languages:]
  C, C++, C\#, CSS, Haskell, HTML, Java, Javascript, \LaTeX, Matlab, MEL, Perl, PHP, Prolog, Python, R, Ruby, Shell script, SQL
\item[Frameworks:]
  Catalyst, Django, Rails, Laravel, XNA, Yesod
\item[Operating Systems:]
  Windows, Linux
\item[Aplications:]
  3D Studio Max, After Efects, Autocad, Blender, Maya, Photoshop, Unity, Microsoft Office Word, Excel, PowerPoint, Publisher
\item[Others:]
  Git, Heroku
  
\end{description*}
\end{indentsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                 Abilities and Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hrule
\vspace{-0.4em}
\subsection*{Abilities and Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}

\item
  Proactive attitude
\item
  Willingness to learn new skills
\item
  Creativity and innovation available
\item
  Ability to assume responsibilities
\item
  Ability to work in team
\item
  Easy to work with public
\item
  Working under pressure

\end{description*}
\end{indentsection}


\end{document}